### 2019-06-23 TFM.tex
Parte combinatoria acabada

\usepackage[left=4cm,right=4cm,top=3cm,bottom=3cm]{geometry}
\usepackage{graphicx}
\usepackage{amssymb,mathtools, amsmath, amsfonts, amsthm}
%\usepackage{color}
\usepackage{float}
\usepackage{hyperref}
\usepackage{enumerate}
\usepackage{enumitem}

@@

\newtheorem{proposition}{Proposition}[chapter]
\newtheorem{fact}{Fact}[chapter]
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{lemma}{Lemma}[chapter]
\newtheorem{corollary}{Corollary}[chapter]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[chapter]
\newtheorem{propdef}{Proposition / Definition}[chapter]

@@

Define the families of expressions with arguments $\beta_1,\dots, \beta_l$: 
$\Lambda$, $\mathcal{E}$ and $\Theta$. \par
For any sentence $\phi$ we use the notation 
$Pr_n(\phi):=Pr(G\models \phi)$. \par
For any F.O. formula $\phi(x_1,\dots,x_l)$ with free variables 
$x_1, \dots, x_l$, we define $Pr_n(\phi(x_1,\dots,x_l))=
\sum_{G\models \phi(a_1,\dots,a_l)} Pr_n(G) $, 
where $a_1, \dots, a_l$ are fixed natural numbers in $[n]$.

\begin{theorem}

@@

\begin{theorem} 
	Let $\phi(x_1,\dots, x_l)$ be a consistent open formula, and let $k,r,s\in \N$ $s\leq l$. Then for any $k$-morphism classes of trees with radii
	at most $r$ the limit
	\[ \Ln Pr(\bigwedge_{i=i}^s Tree_r(x_i,G)\in C_i \, | \, \phi(x_1,\dots, x_l) \,)\]
	exists and belongs to $\Lambda$.	
\end{theorem}

>>>>

\usepackage[left=4cm,right=4cm,top=3cm,bottom=3cm]{geometry}
\usepackage{graphicx}
\usepackage{amssymb,mathtools, amsmath, amsfonts, amsthm}
%\usepackage{color}
\usepackage{float}
\usepackage{hyperref}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{chngcntr}

\counterwithout{equation}{section}
\counterwithout{equation}{chapter}

@@

\newtheorem{proposition}{Proposition}[chapter]
\newtheorem{fact}{Fact}[chapter]
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{lemma}{Lemma}[chapter]
\newtheorem{corollary}{Corollary}[chapter]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[chapter]
\newtheorem{propdef}{Proposition / Definition}[chapter]
\theoremstyle{remark}
\newtheorem{remark}{Remark}[chapter]

@@

Define the families of expressions with arguments $\beta_1,\dots, \beta_l$: 
$\Lambda$, $M$ and $\Theta$. \par
For any sentence $\phi$ we use the notation 
$Pr_n(\phi):=Pr(G\models \phi)$. \par
For any formula $\phi$ with free variables 
$x_1, \dots, x_l$, we define $Pr_n(\phi(x_1,\dots,x_l))=
\sum\limits_{G\models \phi(a_1,\dots,a_l)} Pr_n(G) $, 
where $a_1, \dots, a_l$ are fixed \textbf{different}
natural numbers in $[n]$. If $\phi$ and $\sigma$ are 
formulas with possibly some free variables, then we define
$Pr_n(\phi \, | \sigma)=Pr_n(\phi\wedge \sigma)/Pr_n(\sigma)$. \par

We introduce some notation now. For any numbers $l,r\in \N$ 
we denote by $\phi_r(x_1,\dots, x_l)$ the formula
with free variables $x_1,\dots, x_l$
satisfying $G\models \phi_r(x_1,\dots, x_l)$ 
if for any $y$ there is a unique
(minimal) path from $y$ to the set of $x_i$'s.

\begin{lemma}
	Let $\sigma$ be an open formula (i.e., a formula with no quantifiers)
	with free variables $x_1, \dots, x_l$. Then, for any $r\in \N$
	\[ \Ln Pr_n(\phi_r(x_1, \dots x_l) \, | \sigma ) =1 .\]
\end{lemma}
\begin{proof}
	We will se that
	\[ \Ln Pr_n(\neq \phi_r(x_1, \dots, x_l) \, | \sigma ) =0.\]
	Fix $n$ and $x_1,\dots, x_l \in [n]$.
    Notice that without loss of generality we can
	assume that $\sigma$ Boolean combination of atomic
	formulas of the form $R_i(y_1,\dots,y_{a_i})$, where the $y_i$'s
	are among the free variables $x_1,\dots, x_l$.
	In particular $G\models \sigma(x_1, \dots, x_l)$ and 
	$G\models \phi_r(x_1,\dots, x_l)$
	are independent events, because $\phi_r$ depends
	only on the edges not in $x_1,\dots, x_l$.
	Thus, $Pr_n(\neg \phi_r \, | \sigma)= Pr_n(\neg \phi_r)$.
	Consider $G$ a random graph in $G(n,p(n))$. 
	If $\phi_r$ is not satisfied in $G$ then 
	there exists a $y$ different from the $x_i$'s
	and two paths $P_1,P_2$ between $y$ and the set 
	of $x_i$'s with $V(P_i)\leq r+1$. We have two cases
	\begin{itemize}[leftmargin=*]
		\item $P_1$ and $P_2$ contain some vertex $z\neq y$
		in their intersection. Then, using that
		$ch(P_1), ch(P_2)\geq -1$ and counting we get that
		$P_1\cup P_2$ is a critical graph of size no greater
		than $2r+1$.
		\item The union $P_1\cup P_2$ is a path
		between some $x_{i_1}, x_{i_2}$ of size no greater
		than $2r+1$ that contains vertices different
		from the $x_j$'s. Let us denote by $A$ the event that
		such a path exists. One can check that $Pr_n(A)\leq C/n$
		for some fixed $C$.   	
	\end{itemize}
	Thus, if we denote by $B$ the event that $G$ contains some 
	super-critical subgraph of size no greater than $2r+1$,  by the
	union bound:
	\[ Pr_n(\neq \phi_r)\leq  Pr_n(B)+ Pr_n(A) 
	\stackrel{n\to \infty}{\longrightarrow}	0.\]
\end{proof}

\begin{theorem}{(Multivatiate Brun's Sieve)}
	Let $r\in \N$ and for each $i=1,\dots, r$  let
	$\{X_i(n)\}_{n\in \N}$ be a succession of random variables 
	such that for each $n\in \N$, $X_i(n)$ 
	is a sum of random indicator variables (i.e. variables 
	taking only values $0$ and $1$)
	$Y_{i,1}(n),\dots, Y_{i,s_n}(n)$. Let $\lambda_1, \dots ,
	\lambda_r$ be real numbers. If for each 
	$r$-tuple of natural numbers $a_1,\dots, a_r$
	is satisfied
	\[ \Ln E\left[\prod_{i=1}^r \binom{X_i}{a_i} \right] = 
	\prod_{i=1}^r \frac{\lambda_i^{a_i}}{a_i!}, \]
	then the random variable$(X_1,\dots ,X_r)$ converges in distribution
	to a tuple of independent Poisson variables with means $\lambda_1
	\dots \lambda_r$. That is,	
	\[ \forall x_1,\dots, x_r\in \N: \quad \Ln Pr(\wedge_{i=1}^r
	 X_i=x_i)= \prod_{i=1}^r Poi_{\lambda_i}(x_i).\]

@@

\begin{remark}
	Let $X$ be a random variable sum of indicator variables
	$Y_1, \dots, Y_s$. For each $i\in \N$, let 
	$X_i$ be the random variable
	\[X_i= |\{ (j_1,\dots, j_l)\, | \, j_1<\dots<j_i, \, Y_{j_1}=
	\dots = Y_{j_i}=1 \, \}|.\]
	That is, $X_i$ counts the unordered $i$-tuples of $Y_j$'s that 
	take value $1$. Then it is not difficult to check that
	\[ \binom{X}{i}= X_i, \text{ for all } i\in \N. \] 
\end{remark}

Let $x_1, \dots, x_l$ be vertices of a random graph $G$.
For each $y\in V(G)$ we abbreviate by $T_r(y; x,1_,\dots, x_l)$
the rooted tree 
\[Tree(y, Core(G(c_1[x_1],\dots, c_l[x_l]);r)).\]

\begin{theorem} 
	Let $\sigma(x_1,\dots, x_l)$ be a consistent open formula, and let $k,r,s\in \N$ $s\leq l$. Then, for any $k$-morphism classes $C_1, 
	\dots, C_s$ of trees with radii
	at most $r$ it is satisfied
	\[ \Ln Pr_n(\bigwedge_{i=1}^s Tree_r(x_i; x_1, \dots, x_l)\in C_i \, | 
	\, \sigma(x_1,\dots, x_l) \,)= \prod_ {i=1}^s \lambda_{C_i,r}.\]	
\end{theorem}
\begin{proof}
The proof is by induction on $r$.

	\item For $r=0$ there is only one class
	of $k$-morphic trees and the probability in 
	the statement is always $1$ for all $n$.
	\item Fix $r>0$ and assume that the statement
	is true for all lesser values of $r$. \par
%	Because of lemma REF
%	\begin{align*} 
%	&\Ln Pr_n(\bigwedge_{i=1}^s T_r(x_i; x_1, \dots, x_l)\in C_i \, | 
%	\,\sigma \,)= \\
%	&=\Ln Pr_n(\bigwedge_{i=1}^s T_r(x_i; x_1, \dots, x_l)\in C_i \, | 
%	\, \sigma \wedge \phi_r(x_1,\dots,x_l)\,).
%	\end{align*}
	Let $\mathcal{E}$ be the set of $k$-types of edges $E$ of
	radius at most $r-1$. For each $E\in \mathcal{E}$
	pick a representative
	$( C_{E,1}, \dots, C_{E,j-1}, r, C_{E,j}\dots, C_{E,a_E-1})$, 
	and denote by $j_E$ the index of the root in that representative. 
	Denote by $a_E$ and $c_E$ the arity and color of $E$, and 
	denote by $\psi_E$ the subgroup of the symmetry group of $\phi_{c_E}$ 
	that fixes the index $j_E$.
	Consider, for each $i=1,\dots, s$ and each the random variables 
	\[X_{i,E}(n)= \text{number of initial edges of type }E \text{ in } 
	T_r(x_i;x_1, \dots, x_l). \]

	Given $e=[y_1,\dots,y_{j_E-1},x_i, y_{j_E},\dots ,y_{a_E-1}]\in \mathcal{H}_{c_E}(n)$ we can define the indicator 
	random variable $X_{i,E,e}$ that takes value $1$ if the following are 
	all satisfied
	\begin{itemize}
		\item $e\in H_{c_E}$,
		\item $e$ belongs to $T_r(x_i;x_1, \dots, x_l)$, and
		\item the $k$-type of $e$ is $E$. 	
	\end{itemize} 
	One can check that for fixed $i, E$
	\[X_{i,E}(n)= \sum_{e=[y_1,\dots,y_{j_E-1},x_i,y_{j_E},
	\dots ,y_{a_E-1}]\in \mathcal{H}_{c_E}(n)} X_{i,E,e}(n).\]
	Thus we can apply the multivariate Brun's Sieve to the variables 
	$X_{i, E}$.\par

	Let $(b_{i,E})_{\substack{i=1,\dots, s \\ E\in \mathcal{E}}}$ be 
	natural numbers. We want to compute
	\[\Ln E\left[\prod_{i=0}^{s}\prod_{E\in \mathcal{E}}
	\binom{X_{i,E}(n)}{b_{i,E}} \, \Bigg| \, \sigma \right]. \]
	Define by $\Omega$ the set
	\begin{align*}
		&\Omega:= \{ (i,E,b,j) \, | \, i,b,j \in \N, \, E\in \mathcal{E},\\ 
		& 1\leq i \leq s, \, b=1\leq b \leq b_{i,E}, \, 1\leq j \leq a_E-1 \,\}. 
	\end{align*} 
	And let $\hat{\Omega}$ be the projection of $\Omega$ onto its first
	three coordinates. That is,
		\begin{align*}
	&\widehat{\Omega}:= \{ (i,E,b) \, | \, i,b \in \N, \, E\in \mathcal{E},\\ 
	& 1\leq i \leq s, \, b=1\leq b \leq b_{i,E}\,\}. 
	\end{align*}

	Denote by $X$ be the set $\{x_1,\dots,x_l\}$.
	Choose a function $y: \Omega \rightarrow [n]\setminus X$. 
	Informally, $y()$ represents a choice of edges in $G$. We
	say that $y()$ satisfies the property $P$ if for any fixed
	$1\leq i\leq s$, $E\in \mathcal{E}$ and 
	$1\leq b_1 < b_2\leq b_{i,E}$, and $t=1,2$, the tuples
	\[ [y(i,E,b_t,1),\dots, y(i,E,b_t,j_E-1), x_i, y(i,E,b_t,j_E),\dots
	y(i,E,b_t,a_E-1)] \]
	represent different elements in $\mathcal{H}_{c_E}(n)$.
	In other words, $y()$ is a choice of different edges. \par	
	Define
	the event $A(y)$ as
	\[ \bigwedge_{(i,E,b,j)\in \Omega} y(i,E,b,j)\in T_r(x_i;x_1, \dots, x_l) .\]
	Define also the event $B(y)$ as 
	\[\bigwedge_{\omega=(i,E,b)\in \widehat{\Omega}} [y(\omega,1), \dots, 
	y(\omega,j_E-1), \, x_i \, ,y(\omega,j_E),\dots,  y(\omega,a_E-1)]\in H_{c_E} .\]
	Finally, let $T(y)$ be the event that
	\[\bigwedge_{(i,E,b,j)\in \Omega} T_{(r-a_E+1)}(y(i,E,b,j);x_1
	\dots,x_l)\in C_{E,j}.\]
	That is, 
	\begin{itemize}[leftmargin=*]
		\item  $A(y)$ is the event that for any fixed $(i,E,b)$ the vertices $y(i,E,b,j)$ belong to the tree of $x_i$, 
		\item  $B(y)$ is the event that for any fixed $(i,E,b)$ 
		the vertices $y(i,E,b,j)$ together with $x_i$ form an edge in 
		$H_{c_E}$ when ordered in a particular way, and
		\item $T(y)$ is the event that the tree hanging from
		each vertex $y(i,E,b,j)$ belongs to the particular $k$-morphism
		class given by the edge type $E$ and the position $j$. 	 	 
	\end{itemize}
	Then it is satisfied

	\begin{align} \nonumber
		& E\left[\prod_{i=0}^{s}\prod_{E\in \mathcal{E}}
		\binom{X_{i,E}}{b_{i,E}} \, \bigg|\, \sigma \right]= \\
		&=\prod_{i=1}^{s}
		\prod_{E\in \mathcal{E}} \left(\frac{1}{|\psi_E|^{b_{i,E}} \cdot b_{i,E}!}\right) \cdot
		\sum_{\substack{y:\Omega \rightarrow [n]\setminus X\\ 
		y \text{ satisfies } P}} 
		Pr( T(y) \, \wedge \, A(y) \wedge \, B(y) \, | \, \sigma \, ).		
	\end{align} 
	Notice that $A(y)$ implies that $y$ is injective. Indeed, if a vertex
	$v$ belongs to two edges incident to some $x_i$ then both edges cannot
	belong to the tree of $x_i$ because they would form a cycle (or a super-critical graph). Also, if $v$ belongs to the edges $e_1, e_2$
	incident to $x_i$ and $x_j$ respectively then it cannot happen that
	$e_1$ is in the tree of $x_i$ and $e_2$ is in the tree of $x_j$ at the
	same time, because $e_1\cup e_2$ would belong to the center of 
	$Core(G(c_i[x_i],c_j[x_j]);r)$.
	In consequence we only need to take in consideration injective $y$'s in 
	last equation. Also, by the symmetry of the random model, the probability
	written in that equation is equal for all injective $y$'s. 
	Hence we have
	\begin{align} \nonumber
		& \prod_{i=1}^{s}
		\prod_{E\in \mathcal{E}} \left(\frac{1}{|\psi_E|^{b_{i,E}} \cdot b_{i,E}!}\right) \cdot
		\sum_{\substack{y:\Omega \rightarrow [n]\setminus X\\ y \text{ injective}}} 
		Pr( T(y) \, \wedge \, A(y) \wedge \, B(y) \, | \, \sigma \, )=\\
		& \label{eqn:distributed}
		\prod_{i=1}^{s}
		\prod_{E\in \mathcal{E}} \left(\frac{1}{|\psi_E|^{b_{i,E}} \cdot b_{i,E}!}\right) \cdot
		Pr( T(z) \, \wedge \, A(z) \wedge \, B(z) \, | \, \sigma \, )
		\cdot \sum_{\substack{y:\Omega \rightarrow [n]\setminus X\\ y \text{ injective}}} 1,
	\end{align} 
   	where $z$ is an arbitrary injective map from $\Omega$ to
   	$[n]\setminus X$. \par
	We can write
	\[Pr( T(z) \, \wedge \, A(z) \wedge \, B(z) \, | \, \sigma \, )=
	Pr( T(z) \, \wedge \, A(z) \, | \, B(z) \wedge \sigma \, )
	\cdot Pr( \, B(z) \, | \, \sigma \, )\]
	Notice that $\phi_r(x_1,\dots, x_l)\wedge B(z)$ implies $A(z)\wedge
	B(z)$,	and in consequence the following chain of inequalities holds
	\begin{align*} 
	Pr( T(z)  \, | \, B(z) \wedge \sigma \, ) &
	\geq Pr( T(z) \wedge A(z)  \, | \, B(z) \wedge \sigma \, ) \geq \\ 
	& \geq Pr(T(z) \wedge \phi_r(x_1,\dots,x_l) 
	\, | \, B(z) \wedge \sigma \, ).
	\end{align*}
	But using lemma REF we get
	\[ \Ln  Pr_n(T(z) \wedge \phi_r(x_1,\dots,x_l)
	\, | \, B(z) \wedge \sigma \, ) = 
	\Ln Pr_n(T(z)\, | \, B(z) \wedge \sigma \, ), \]
	so
	\begin{equation} 
	\Ln  Pr_n(T(z) \wedge A(z)
	\, | \, B(z) \wedge \sigma \, ) = 
	\Ln Pr_n(T(z)\, | \, B(z) \wedge \sigma \, ). 
	\end{equation}
 	Notice that $B(z)$ can be written in terms of a purely relational
 	open formula with free variables the $y(i,E,b,j)$'s.
 	Thus by the induction hypothesis we have
 	\[\Ln Pr_n( T(z)  \, | \, B(z) \wedge \sigma \, )= \Gamma, \]
 	where 
 	\begin{equation}\label{eqn:gammadef}
 	\Gamma:=\prod_{\substack{1\leq i \leq s \\ E\in \mathcal{E}\\
 	1\leq j \leq a_E - 1 }} (\lambda_{C_{E,j}})^{b_{i,E}}.
 	\end{equation}
 	In particular $\Gamma$ is different from $0$.
 	Hence, last term in \cref{eqn:distributed} is equal to
 	\begin{equation} \label{eqn:distributed2}
 	\Ln	\prod_{i=1}^{s}
 		\prod_{E\in \mathcal{E}} \left(\frac{1}{|\psi_E|^{b_{i,E}} \cdot b_{i,E}!}\right) 
 		\cdot \Gamma \cdot
 		Pr_m(\, B(z) \, | \, \sigma \, )
 		\cdot \sum_{\substack{y:\Omega \rightarrow [n]\setminus X\\ y \text{ injective}}} 1.
 	\end{equation} 
 	Also,
 	\[\sum_{\substack{y:\Omega \rightarrow [n]\setminus X\\ y \text{ injective}}} 1 =|[n]\setminus X|\cdot (|[n]\setminus X|)\cdots 
 	(|[n]\setminus X|-|\Omega|+1), \]
 	and using that $X$ and $\Omega$ are constant in size,
 	\begin{equation}\label{eqn:sumones}
 	\sum_{\substack{y:\Omega \rightarrow [n]\setminus X\\ y \text{ injective}}} 1 \simeq n^{|\Omega|},
 	\end{equation}
 	where $f(n)\simeq g(n)$ means that $\Ln f(n)/g(n)=1$.
 	Finally, as $\sigma$ only affects the edges between the $x_i$'s
 	, $B(z)$ and $\sigma$ are independent. Hence,
 	\[ Pr_n(\, B(z) \, | \, \sigma \, ) = \prod_{i=1}^{s} 
 	\prod_{E\in \mathcal{E}} \left(\frac{\beta_{c_E}}{n^{(a_E -1)}}
 	\right)^{b_{i,E}},  \]
 	and using that
 	\[  n^{|\Omega|}= \prod_{i=1}^{s} 
 	\prod_{E\in \mathcal{E}} (n^{(a_E-1)})^{b_{i,E}}  \]
 	and \cref{eqn:sumones} we obtain 
 	\begin{equation} \label{eqn:substitution}
 	Pr_n(\, B(z) \, | \, \sigma \, )\cdot \sum_{\substack{y:
 	\Omega \rightarrow [n]\setminus X\\ y \text{ injective}}} 1 \simeq 	
 	\prod_{E\in \mathcal{E}} \beta_{c_E}^{b_{i,E}}. 
 	\end{equation}
 	In consequence, using \cref{eqn:substitution} and \cref{eqn:gammadef} in
 	\cref{eqn:distributed2} we get
 	\[ \Ln E\left[\prod_{i=0}^{s}\prod_{E\in \mathcal{E}}
 	\binom{X_{i,E}}{b_{i,E}} \, \Bigg| \, \sigma \right]= \prod_{i=0}^{s}\prod_{E\in \mathcal{E}}
 	\left[ 	\left(\frac{\beta_{c_E} \prod_{j=1}^{a_E -1} \lambda_{C_{E,j}} }{|\psi_E|}\right)^{b_{i,E}} \frac{1}{b_{i,E}!} \right]. \]
 	And using the multivariate Brun's Sieve we get that for each
 	choice of natural numbers $\{b_{i,E}\}_{\substack{1\leq i \leq s\\ 
 	E\in \mathcal{E}}}$ it is satisfied
 	\[ \Ln Pr_n\left(\bigwedge_{i=0}^{s}\bigwedge_{E\in \mathcal{E}} X_{i,E}=b_{i,E} \, \Bigg| \, \sigma \right) = 
 	\prod_{i=0}^{s}\prod_{E\in \mathcal{E}} Poi_{\mu_E}(b_{i,E}),\]
 	where
 	\[\mu_E=
 	\frac{\beta_{c_E} \prod_{j=1}^{a_E -1} \lambda_{C_{(E,j)},(r-a_E+1)} }{|\psi_E|}.\]
 	The $k$-morphism class of $T_r(x_j;x_1, \dots, x_l)$ depends exclusively
 	on the number, up to $k+1$, of its initial edges of each type.
 	More explicitly
 	\begin{align*}
 	&T_r(x_j;x_1, \dots, x_l)\in C \iff \\
 	& \bigwedge_{E\in \mathcal{E}}
 	\big(X_{j, E}= (C,E) \text{  if  } (C,E)\leq k \big),
 	\text{  or  }  \big(X_{j, E}\geq k+1 \text{ otherwise}\big). 
 	\end{align*}
 	In consequence 
 	\begin{align*}
 	&\Ln Pr_n(\bigwedge_{i=1}^s Tree_r(x_i; x_1, \dots, x_l)\in C_i \, | 
 	\, \sigma \,)=\\ 
 	&=\prod_{i=0}^{s}\left[
 	\left(\prod_{\substack{E\in \mathcal{E}\\ (C_i,E)<k+1}} Poi_{\mu_E}((C_i,E))\right)
 	\left(\prod_{\substack{E\in \mathcal{E}\\ (C_i,E)\geq k+1}} 
 	Poi_{\mu_E}(\geq (k+1))\right)\right]=\\
 	&=\prod_{i=0}^{s} \lambda_{C_i,r},
    \end{align*}
 	as we wanted. 
%n^{\sum_{i=1}^s
%	\sum_{E\in \mathcal{E}} b_{i,E}\cdot(a_{E}-1)}

 	%\[	Pr( T(z) \, \wedge \, A(z) \, | \, B(z) \wedge \sigma \, )
 	%\cdot Pr( \, B(z) \, | \, \sigma \, )=	Pr( T(z) \, | \, B(z) \wedge %\sigma \, )
 	%\cdot Pr( \, B(z) \, | \, \sigma \, )\]

 %  \[ \phi_r(x_1,\dots, x_l)\wedge T(z)\wedge B(z)\implies 
 % T(z)\wedge A(z) \wedge B(z).\]
 %  Also, if by lemma REF, for any formula $\alpha$ with possibly 
 %  some free variables,
 % \[ Pr_n(\, \alpha \wedge \phi_r \, | \, \sigma \,) \simeq
 %  Pr_n(\, \alpha \, |\, \phi_r \wedge \sigma \,) .\]
 %  , where the notation  $ f(n)\simeq \ g(n)$, for maps $\N\rightarrow %\R$ satisfying that $g$ takes non-zero
 %  values when $n$ is sufficiently large. We will use the notation
 %   $f\simeq g$ to mean $\Ln f(n)/g(n)=1$. \par

%   \begin{align*}
%   &\Ln Pr_n ( T(z) \, \wedge \, A(z) \wedge \, B(z) \, | \, \sigma \, )
%   \simeq \\
%   &\Ln Pr_n ( T(z) \, \wedge \, B(z) \, | \, \phi_r(x_1, \dots, x_l)\, 
%   \wedge \, \sigma \, ) = \\
%   &\Ln Pr_n ( T(z) \, | \, \phi_r \, 
%   \wedge \, \sigma \, \wedge \, B(z) \, )\cdot
%   Pr_n(B(z)\, | \, \phi_r \, 
%   \wedge \, \sigma \,) \simeq \\
%   &\Ln Pr_n ( T(z) \, | \, \phi_r \, 
%   \wedge \, \sigma \, \wedge \, B(z) \, )
%   \prod_{E\in\mathcal{E}}\bigg(\frac{\beta_{c_E}}{n^{a_E-1}}\bigg)^{b_{i,E}}
%   \end{align*}
%   
%   
%   
%
%	Also, by lemma REF, for any formula $\alpha$  
%	with possibly some free variables,
%	and any	$r\in \N$, $r>0$, we have
%	\[\Ln Pr_n(\alpha \, | \, \sigma(x_1,\dots, x_l))
%	= \Ln Pr_n(\alpha \, | \, \phi_r(x_1,\dots, x_l)\wedge \sigma ).\]
%

\begin{theorem}
	Let $O$ be a simple $k$-agreeability class. Then it is satisfied
	\[ \Ln Pr_n(Core(G;r)\in O) = \theta, \]
	for some $\theta\in \Theta$.
\end{theorem}

\begin{proof}
	This is an easier version of last theorem. \par
	Let $\mathcal{U}$ be the set of all $k$-morphism classes of 
	unicycles with radius at most $r$. 
	For each class $U\in \mathcal{U}$ choose a representative $rep(U)\in U$, 
	and let  $cycle(U)$ be the cycle in $rep(U)$, whose number of vertex will be
	denoted by $n_U$. Choose an ordering $x_{U,1},\dots, x_{U,n_U}$
	of the vertices in $cycle(U)$ and for each $1\leq i \leq n_{U}$ 
	denote by $C_{U,i}$ the $k$-morphism class
	of $Tree(x_i,rep(U))$. One can consider $cycle(U)$ to be a 
	vertex colored graph where the color assigned to each vertex $x_i$
    is $C_{U,i}$. Isomorphisms of the colored cycle 
	$cycle(U)$ induce permutations of $[n_U]$ via this ordering. 
	Let us denote by $\psi_U$ that group of permutations.\par 
	For any $U\in \mathcal{U}$ we define the random variable 
	\[X_{U}(n)=\text{number of connected components of }Core(G;r) 
	\text{ in } U ,\]
	and for each element $g\in V(G)^{n_U}/\psi_U$ 
	we define the indicator variable $X_{U,g}(n)$ that equals $1$ if 
	\begin{itemize}
		\item $g=[x_1,\dots, x_{n_U}]$, for some vertices
		$x_1,\dots, x_{n_U}$ such that the map $f:G[X]\rightarrow cycle(U)$ 
		,where $X=\{x_1,\dots x_{n_U}\}$, defined by $x_i\mapsto x_{U,i}$ is an
		isomorphism. 
		\item $N(X;r)$ is a connected component of $Core(G;r)$.
		\item $N(X;r)\morph{k} rep(U)$ via $f$. In particular this means
		that $Tree(x_i, G)$ belongs to $C_{U,i}$.
	\end{itemize}	
	In other words, $X_{U,g}$ indicates if there is a graph in the $k$-morphism
	class $U$ embedded in $G$ in a particular way represented by $g$.
	One can check that for all $U\in \mathcal{U}$
	\[ X_U(n)=\sum_{g\in [n]/\psi_U} X_{U,g}(n),  \]
	so we can apply the multivariate Brun's Sieve to the $X_U$'s.\par
	Let $(b_U)_{U\in \mathcal{U}}$ be fixed natural numbers. We are interested
	in obtaining
	\[\Ln E\left[\prod_{U\in \mathcal{U}}
	\binom{X_{U}(n)}{b_{U}}\right].\]
	Let $\Omega$ be the set defined as
	\[ \Omega:= \{\, (U,b,i) \, | \, U\in \mathcal{U}, 
	\, b,i\in \N, \, 1\leq b \leq b_U,  \, 1\leq i \leq n_U\,  \}\]
	and let $\widehat{\Omega}$ be the projection of $\Omega$ onto its
	two first coordinates. That is, 
	\[\widehat{\Omega}:=\{\, (U,b) \, | \, U\in \mathcal{U}, 
	\, b\in \N, \, 1\leq b \leq b_U \, \}. \]

	Let $y: \Omega \rightarrow [n]$ be a map. Informally, $y()$
	represents a choice of embeddings of graphs in with the appropriate
	$k$-morphism classes. We will say that $y()$ satisfies the property
	$P$ if for any fixed $U\in \mathcal{U}$ and $1\leq b_1<b_2\leq b_{U}$
	the tuples
	\[ [y(U,b_1,1), \dots, y(U,b_1,n_U)], \text{ and }
	[y(U,b_2,1), \dots, y(U,b_2,n_U)] \]
	represent different elements in $[n]^{n_U}/\psi_U$. That is, $y()$ is 
	a choice of different embeddings.\par
	Define for any $(U,b)\in \widehat{\Omega}$
	the set $Y(U,b)=\{ \, y(U,b,i) \, | \, 1\leq i \leq n_U \, \}$.

	We define the following events for a given $y:\Omega\rightarrow [n]$.
	\begin{itemize}
		\item Let $A(y)$ be the event that for each $(U,b)\in \widehat{\Omega}$,
		the map $f_{U,b}:cycle(U)\rightarrow G[Y(U,b)]$ given
		by $x_{U,i} \rightarrow y(U,b,i)$ is an embedding. 	
		\item Let $B(y)$ be the event that $Center(N(Y(U,b);r)$ is 
		the image of $f_{U,b}$,	for each $(U,b)\in \widehat{\Omega}$.
		\item Let $T(y)$ be the event that 
		\[\bigwedge_{(U,b,i)\in \Omega} T_r(y(U,b,i); Y)\in C_{U,i}, \]
		where $Y$ denotes set of vertices in the image of $y$.  
	\end{itemize}
	Then,
	\[ E\left[\prod_{U\in \mathcal{U}}
	\binom{X_{U}(n)}{b_{U}}\right] = \prod_{U\in \mathcal{U}} 
	\frac{1}{|\psi_U|^{b_U}b_U!} \cdot
	\sum_{\substack{y:\Omega \rightarrow [n]\\y \text{ satisfies }P}}
	Pr(A(y)\wedge B(y)\wedge T(y)). \]

	Property $P$,together with events $A(y)$ and $B(y)$ imply that $y$ is
	injective, so we can consider only such $y$'s in last equation. Again, by 
	the symmetry of the random model the probability appearing there is the same
	for all injective $y$'s. Hence,
	\begin{align}
	\nonumber
	&\prod_{U\in \mathcal{U}} 
	\frac{1}{|\psi_U|^{b_U}b_U!} \cdot
	\sum_{\substack{y:\Omega \rightarrow [n]\\y \text{ satisfies }P}}
	Pr(A(y)\wedge B(y)\wedge T(y))= \\ 
	\label{eqn:distributed3}
	& =\prod_{U\in \mathcal{U}} 
	\frac{1}{|\psi_U|^{b_U}b_U!} \cdot Pr(A(z)\wedge B(z)\wedge T(z)) \cdot
	\sum_{\substack{y:\Omega \rightarrow [n]\\y \text{ injective }}}1,
	\end{align}
	where $z$ is an arbitrary injective map $z:\Omega\rightarrow [n]$.\par
	We can write 
	\[Pr(A(z)\wedge B(z)\wedge T(z))=Pr(B(z)\wedge T(z) \, |\, A(z)) \cdot 
	Pr(A(z)).\]
	Let $\tau_r$ be the event that $G$ is $r$-simple. One can check that
	$A(y) \wedge \tau_r$ implies $A(y)\wedge B(y)$. 
	In consequence the following chain of inequalities holds
	\[Pr(T(z)\,|\, B(z))\geq Pr(T(z)\wedge A(z) \,| \, B(z)) \geq
	 Pr(T(z)\wedge \tau_r \,| \, B(z)).\]
	Notice that $B(z)$ can be expressed as a purely relational open formula
	with free variables the elements indexed by $z$, because it only depends on
	the edges between vertices in the image of $z$.
	Using the previous theorem and LEMMA we obtain
	\[\Ln Pr_n(T(z)\wedge \tau_r \,| \, B(z))= \Ln Pr_n(T(z)| \,| \, B(z)) = \Gamma, \]
	where
	\[ \Gamma:=\prod_{\substack{U\in \mathcal{U}\\ 1 \leq i\leq n_{U}}}
	(\lambda_{C_{(U,i)}, r})^{b_U}.\]

	Because the probability of each edge is independent, one obtains 
	\[ Pr_n(B(z))= \prod_{(U,b)\in \widehat{\Omega}} 
	\frac{\prod_{i=1}^c	\beta_i^{|H_i(cycle(U))|}}{n^{n_U}}.  \]
	Also,
	\[\sum_{\substack{y:\Omega \rightarrow [n]\\y \text{ injective }}}1
	\simeq \prod_{(U,b)\in \widehat{\Omega}} n^{n_U}. \]
	This way substituting REF, REF and REF in EQ we get
	\[\Ln E\left[\prod_{U\in \mathcal{U}}
	\binom{X_{U}(n)}{b_{U}}\right]= \prod_{U\in \mathcal{U}}
	\left(\frac{ \prod_{i=1}^c \beta_i^{|H_i(cycle(U))|} \prod_{i=1}^{n_U} \lambda_{U,i}}{|\psi_U|}\right)^{b_U}\cdot \frac{1}{b_{U}!}. \]

	Applying the multivatiate Brun's Sieve we obtain that for any fixed  
	natural numbers $(b_U)_{U\in \mathcal{U}}$ 
	\[\Ln Pr_n\left( \bigwedge_{U\in \mathcal{U}} X_U=b_U  \right)=
	\prod_{U\in \mathcal{U}}Poi_{\xi_U}(b_i),
	\]
	where
	\[ \xi_U= \frac{ \prod_{i=1}^c \beta_i^{|H_i(cycle(U))|} \prod_{i=1}^{n_U} \lambda_{U,i}}{|\psi_U|}.\]
